%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%%
%%% 
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
\usepackage{fontawesome,url}
\usepackage{datetime}
\usepackage[
  top=0.5in,
  bottom=0.5in,
  left=2in,
  right=1in,
%  headheight=17pt, % as per the warning by fancyhdr
  includehead,includefoot,
  heightrounded % to avoid spurious underfull messages
]{geometry} 
\usepackage{fancyhdr}
\usepackage{lipsum} % only for showing some sample text
\fancyhf{} % clear all header and footers
\renewcommand{\headrulewidth}{0pt} % remove the header rule
\cfoot{\thepage}
\pagestyle{fancy}
%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Frederick Boehm}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Wisconsin-Madison}
\def\myaddress{Statistics Department}
\def\myemail{fjboehm@wisc.edu}
\def\myweb{https://fboehm.us}
\def\myphone{(715) 252-3929}
%\def\myfax{(919) 660-5623}
\def\mytwitter{@fredboehm128}
\def\myversion{}
\def\myrevision{}


\def\myaffiliation{University of Wisconsin-Madison}
\def\myauthor{Frederick Boehm}
\date{} % not used (revision control instead)
\def\mykeywords{Vita, CV, Statistics}

%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%\immediate\write18{sh ./vc}
%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
%\input{vc}

%\newfontfamily\tgtermes{Optima}
%\makeatletter
%  \begingroup
%    \tgtermes
%    \DeclareFontShape{\f@encoding}{\rmdefault}{m}{sc}{%
%      <-> ssub * \f@family/m/sc}{}
%    \DeclareFontShape{\f@encoding}{\rmdefault}{bx}{sc}{%
%      <-> ssub * \f@family/bx/sc}{}
%  \endgroup
%\makeatother




%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	%Ligatures={Common}]{Minion Pro}
	Ligatures={Common}]{Baskerville}
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]{Arial}
\setmonofont[Mapping=tex-text,Scale=0.72]{American Typewriter} 

%\newfontface\scheader[SmallCapsFont={Arial},SmallCapsFeatures={Letters=SmallCaps}]{Arial}

%\newfontface\addressblock[Mapping={tex-text}, 
%	Numbers={OldStyle},
%	Ligatures={Common}]{Minion Pro Medium Caption}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
%\pagestyle{kjh}
%\thispagestyle{kjhgit}


%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{3.95in}
 \flushright {\footnotesize 
 \href{http://www.stat.wisc.edu}{Department of Statistics}, \\ 1300 University Ave., \\ 1220 Medical Sciences Center, \\ \vspace{-0.05in} Madison, \textsc{WI} 53706.}  
  
\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.3in}
  \flushright \footnotesize \myphone \, \faPhone \\ 
  %\flushright \footnotesize  \addressblock \myphone \, \faPhone \\ 
  {\scriptsize  \texttt{\href{http://twitter.com/fredboehm128}{\mytwitter}} \, \faTwitter }  \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}} \, \faGlobe}
\end{minipage}

\medskip

%% Name 
%\noindent{\LARGE\scheader \textsc{Frederick Boehm}}
\noindent{ \textbf{\LARGE{F}\Large{REDERICK}} \textbf{\LARGE{B}\Large{OEHM}}}
\reversemarginpar

\bigskip       


%% Appointments
% \medskip
%\marginhead{\sffamily appointments}

%\ind Associate Professor in Sociology and the Kenan Institute for Ethics, Duke University, 2009--Present.      

%\ind Visiting Associate Professor of Sociology, Duke University, 2008--2009.

%\ind Associate Professor of Sociology, University of Arizona, 2008.

%\ind Research Fellow, Social and Political Theory Program,
%Research School of Social Sciences, Australian National University, 2003--2006.

%\ind Assistant Professor of Sociology, University of Arizona, 2001--2008.

%\bigskip

%% Education

\marginhead{\sffamily {{\vskip -0.23em} education}}

%\noindent\emph{Princeton University \vspace{0.01in}}

\ind Ph.D., Statistics, University of Wisconsin-Madison, 2018 (anticipated).

%\ind \hspace{0.35in} \footnotesize Dissertation: \emph{Exchange in Blood and Organs}.\newline Winner, American Sociological Association's Dissertation Award.\normalsize \vspace{0.05in}

\ind M.D., University of Wisconsin-Madison, 2007. 

%\medskip
%\noindent\emph{National University of Ireland (Cork)\vspace{0.02in}}

\ind M.S., Population Health Sciences, University of Wisconsin-Madison, 2007.

%\ind \hspace{0.35in} \footnotesize Thesis: \emph{The Language of Influence: Public Debate and the Politics of the X-case.} \normalsize \vspace{0.01in}

\ind B.S. with Honors, Chemistry, Mathematics, and Biochemistry, University of Wisconsin-Madison, 2001.

\bigskip
 
%% Publications
\marginhead{\sffamily {\vskip 0.35em} publications}
\medskip
%\noindent\emph{Book \vspace{0.01in}}
%
%\ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{0.05in}
%
%\ind \hspace{0.35in} \footnotesize Winner, Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Outstanding Book Prize. Finalist, C. Wright Mills Award. 
%
%\vspace{-0.075in}
%
%\normalsize

%\bigskip
\noindent\emph{Peer-reviewed journal articles \vspace{0.05in}}
 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Chris Wells, Dhavan V Shah, Jon C Pevehouse, JungHwan Yang, Ayellet Pelled, Frederick Boehm, Josephine Lukito, Shreenita Ghosh, Jessica L Schmidt. 2016. ``How Trump drove coverage to the nomination: Hybrid media campaigning.'' \emph{Political Communication.} 33:~669--676.

\ind Eric C Tauchman, Frederick J Boehm, Jennifer G DeLuca. 2015. ``Stable kinetochore–microtubule attachment is sufficient to silence the spindle assembly checkpoint in human cells.'' \emph{Nature Communications.}

\ind James C Costello, Laura M Heiser, Elisabeth Georgii, Mehmet Gönen, Michael P Menden, Nicholas J Wang, Mukesh Bansal, Petteri Hintsanen, Suleiman A Khan, John-Patrick Mpindi, Olli Kallioniemi, Antti Honkela, Tero Aittokallio, Krister Wennerberg, James J Collins, Dan Gallahan, Dinah Singer, Julio Saez-Rodriguez, Samuel Kaski, Joe W Gray, Gustavo Stolovitzky, et al. 2014. ``A community effort to assess and improve drug sensitivity prediction algorithms.'' \emph{Nature Biotechnology.} 32:~1202--1212.

\ind William F Dove, Alexandra Shedlovsky, Linda Clipson, James M Amos-Landgraf, Richard B Halberg, Kathleen J Krentz, Frederick J Boehm, Michael A Newton, David J Adams, Thomas M Keane. 2014. ``A strategy to identify dominant point mutant modifiers of a quantitative trait.'' \emph{G3: Genes, Genomes, Genetics.} 4:~1113--1121.

\ind Cathy C Laurie, Kimberly F Doheny, Daniel B Mirel, Elizabeth W Pugh, Laura J Bierut, Tushar Bhangale, Frederick Boehm, Neil E Caporaso, Marilyn C Cornelis, Howard J Edenberg, Stacy B Gabriel, Emily L Harris, Frank B Hu, Kevin B Jacobs, Peter Kraft, Maria Teresa Landi, Thomas Lumley, Teri A Manolio, Caitlin McHugh, Ian Painter, Justin Paschall, John P Rice, Kenneth M Rice, Xiuwen Zheng, Bruce S Weir. 2010. ``Quality control and quality assurance in genotypic data for genome‐wide association studies.'' \emph{Genetic Epidemiology.} 34:~591--602.

\ind MC Smith Fawzi, W Lambert, F Boehm, JL Finkelstein, JM Singler, F Leandre, P Nevil, D Bertrand, MS Claude, J Bertrand, M Louissaint, L Jeannis, PE Farmer, AT Yang, JS Mukherjee. 2010. ``Economic risk factors for HIV infection among women in rural Haiti: implications for HIV prevention policies and programs in resource-poor settings.'' \emph{Journal of Women's Health.} 19:~885--892.

\ind Elizabeth E Marchani, Yanming Di, Yoonha Choi, Charles Cheung, Ming Su, Frederick Boehm, Elizabeth A Thompson, Ellen M Wijsman. 2009. ``Contrasting identity-by-descent estimators, association studies, and linkage analyses using the Framingham Heart Study data.'' \emph{BMC Proceedings.} 3:~S102.

\ind Jason E Gestwicki, Laura E Strong, Christopher W Cairo, Frederick J Boehm, Laura L Kiessling. 2002. ``Cell aggregation by scaffolded receptor clusters.'' \emph{Chemistry \& Biology.} 9:~163--169.

%\end{revnumerate}
%\newpage
\bigskip

\noindent\emph{Edited books \vspace{0.05in}}

\ind A Vishnu Moorthy, Bryan Neil Becker, Frederick J Boehm III, Arjang Djamali (eds.). 2009. \emph{Pathophysiology of Kidney Disease and Hypertension.} Saunders/Elsevier.

\bigskip

\noindent\emph{Book chapters \vspace{0.05in}}
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

\ind Kelly Ann Traeger, Frederick J Boehm III, Arjang Djamali. 2009. ``Acid-Base Homeostasis and Metabolic Alkalosis'' in \emph{Pathophysiology of Kidney Disease and Hypertension}, Moorthy et al. (eds.).

\ind Frederick J Boehm III, Kelly Ann Traeger, Arjang Djamali. 2009. ``Metabolic Acidosis and Approach to Acid-Base Disorders'' in \emph{Pathophysiology of Kidney Disease and Hypertension}, Moorthy et al. (eds.).

\ind A. Vishnu Moorthy, Frederick J Boehm III. 2009. ``Urinalysis and an Approach to Kidney Diseases'' in \emph{Pathophysiology of Kidney Disease and Hypertension}, Moorthy et al. (eds.).


%\end{revnumerate}

\bigskip 

%\newpage
\noindent\emph{Other works \vspace{0.05in}}

%\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
%\begin{revnumerate}

\ind Catherine DeRose, Carrie Roy, Fred Boehm. 2014. ``Victorian eyes: Literary, statistical, and artistic perspectives on Victorian novels – and Dickens's unfinished murder mystery.'' \emph{Significance.} 11:~40--43.

\ind Fred Boehm. 1997. ``The lone male wolf of Sandhill Wildlife Area.'' \emph{International Wolf.} 7:~7--9.

% %\end{revnumerate}
 \bigskip

%% Presentations
%\marginhead{\sffamily {\vskip 0.5em}selected \newline invited talks \newline since 2007}
%\medskip
%
%
%\ind ``Classification Situations.'' Yale University Center for Cultural Sociology, 2013.
% 
%\ind ``Scores and Classes.'' University of Pennsylvania, 2012.%
%
%\ind ``The Performativity of Networks.'' Max Planck/Sciences Po Center, Paris, 2012. 
% 
%\ind ``Specialization and Status in Philosophy.'' Princeton University, 2010. 
%
%\ind Invited Discussant, ``For Love or Money?'', Center for the Interdisciplinary Study of Work and Social Capital, Washington University in St.\,Louis School of Law, 2010. 
%
%\ind ``Gift Fetishism and the Market for Human Organs.'' CAL Visiting Scholar Lecture Series, James Madison University, 2009. 
%
%\ind ``Specialization and Status in Philosophy.'' University of Chicago, Booth School of Business, 2009. 
%
%\ind ``Specialization and Status in Philosophy.'' University of California, Berkeley, 2009. 
%
%\ind ``Specialization and Status in Philosophy.'' University of Michigan, ICOS, 2009. 
%
%\ind ``Specialization and Status in Philosophy.'' Columbia University 2009. 
%
%\ind ``The Performativity of Networks.'' Yale University, 2009. 
%
%\ind ``The Performativity of Networks.'' Stanford University Graduate School of Business, 2008. 
%
%\ind ``The Performativity of Networks.'' Harvard/MIT Joint Seminar in Economic Sociology, 2008. 
%
%\ind ``Last Best Gifts: Altruism and the Market for Human Blood and Organs.'' Center for History, Society and Culture, University of California at Davis, 2007. 
%
%\ind ``Gift Fetishism and the Market for Human Organs.'' Department of Anthropology, University of Arizona, 2007. 
%
%\end{revnumerate}

%\bigskip

%\newpage

\marginhead{\sffamily {\vskip 0.5em}selected \newline presentations}
\medskip

\ind Frederick Boehm, Robert Turner, Bret Hanlon. ``Event Detection with Topic Modeling of Tweets.'' Society for Political Methodology 34th annual meeting. Madison, July 2017.

\ind Fred Boehm, Mark Keller, Alan Attie, Mary Rabaglia, Kathy Schueler, Donald Stapleton, Gary Churchill, Brian Yandell, Karl Broman. ``Pleiotropy vs. Close Linkage in the Diversity Outbred Mouse Population.'' The Jackson Laboratory Systems Genetics Short Course. Bar Harbor, October 2016.

\ind Fred Boehm, Mark Keller, Alan Attie, Mary Rabaglia, Kathy Schueler, Donald Stapleton, Gary Churchill, Brian Yandell, Karl Broman. ``Pleiotropy vs. Close Linkage in the Diversity Outbred Mouse Population.'' Computation and Informatics in Biology and Medicine Training Program Retreat. Madison, October 2016.

\ind Frederick Boehm. ``Data Analysis with Topic Models for Communications Researchers.'' Association for Education in Journalism and Mass Communication Annual Meeting. Minneapolis, August 2016.

\ind Frederick Boehm, Robert Turner, Bret Hanlon. ``Event Detection with Social Media Data.'' UseR! Meeting. Stanford, June 2016.

\ind Frederick Boehm, Robert Turner, Bret Hanlon. ``Event Detection with Topic Modeling of Tweets.'' WARF Discovery Challenge Research Symposium. Madison, April 2016.

\ind Frederick Boehm. ``Post-GWAS characterization of breast cancer-associated SNPs.'' University of Wisconsin-Madison Department of Statistics Student Seminar. Madison, November 2012.

\ind Frederick Boehm, Michael Gould, Christina Kendziorski, and Michael Newton. ``Identification of Expression Quantitative Trait Loci among breast cancer-associated SNPs.'' Computation and Informatics in Biology and Medicine Training Program Retreat. Madison, October 2012.

\ind Frederick Boehm. ``Identification of Expression Quantitative Trait Loci among breast cancer-associated SNPs.'' Molecular and Environmental Toxicology Center Seminar. Madison, September 2012.


\ind Frederick Boehm. ``Identification of Expression Quantitative Trait Loci among breast cancer-associated SNPs.'' Molecular and Environmental Toxicology Center Retreat. Madison, May 2012.


\bigskip 

\marginhead{\sffamily {\vskip 0.6em}grants,\newline honors, \newline \& awards}
\medskip

\ind IRES Research Ethics Fellowship, University of Wisconsin-Madison, 2013-2014.

\ind New Arts Venture Challenge Award for Victorian Eyes art exhibition, University of Wisconsin-Madison, 2013.

\ind Medical Student Research Training Fellowship, Howard Hughes Medical Institute, 2006 (declined due to security concerns in Haiti).

\ind Shapiro Award for research with Partners in Health, University of Wisconsin-Madison, 2004.

\ind Department of Family Medicine LOCUS stipend for research with Partners In Health, University of Wisconsin-Madison, 2004.

\ind Graduate Research Fellowship, National Science Foundation, 2001.

\ind Meyerhoff Excellence Award, University of Wisconsin-Madison, 2001.

\ind University Book Store Award for Outstanding Undergraduate Thesis, 2001.

\ind Department of Chemistry Edward Panek Memorial Scholarship, University of Wisconsin-Madison, 2000.

\ind Hilldale Undergraduate Research Fellowship, University of Wisconsin-Madison, 1999.

\ind Wisconsin Idea Fellowhsip for the Salvation Army Learning Center, University of Wisconsin-Madison, 1999.

\ind Department of Chemistry Summer Research Scholarship, University of Wisconsin-Madison, 1998.

\ind Dean's List, University of Wisconsin-Madison, Spring 1997, Spring 1998 to Spring 2001.

\ind College of Letters \& Science Honors Program, University of Wisconsin-Madison, 1996 to 2001.

\ind Wisconsin Academic Excellence Scholarship, University of Wisconsin-Madison, 1996 to 2000.

\bigskip 


\marginhead{\sffamily {\vskip 0.5em}teaching}
\medskip

\ind ``The College Classroom: How to teach inclusively for educating a diverse nation.'' Co-facilitator. Spring 2017. University of Wisconsin-Madison.

\ind ``Introductory statistics for biologists.'' Lecturer student assistant (Instructor of record). Fall 2016. University of Wisconsin-Madison.

\ind ``Data science.'' Guest lecturer on topic models. Fall 2016. University of Wisconsin-Madison.

\ind ``Data science.'' Teaching assistant. Fall 2016. University of Wisconsin-Madison.

\ind ``Introductory statistics for engineers.'' Lecturer student assistant (Instructor of record). Spring 2014, Fall 2014, Spring 2015, Fall 2015, Spring 2016. University of Wisconsin-Madison.

\ind ``Introductory statistics.'' Lecturer student assistant (Instructor of record). Summer 2015. University of Wisconsin-Madison.

%\item Course: Biostatistics 518: Introduction to biostatistics\\
%Title: Teaching assistant\\
%Term: Winter 2010
%Institution: University of Washington
%\item Course: Biostatistics 517: Introduction to biostatistics\\
%Title: Teaching assistant\\
%Term: Fall 2009\\
%Institution: University of Washington
%\item Course: Biostatistics 511\\
%Title: Teaching assistant\\
%Term: Summer 2008\\
%Institution: University of Washington
%\item Course: Chemistry 3B: Introductory organic chemistry\\
%Title: Graduate student instructor\\
%Term: Fall 2001\\
%Institution: University of California-Berkeley



\bigskip

\marginhead{\sffamily {\vskip 0.5em}service}
\medskip

\noindent\emph{University service \vspace{0.05in}}

\ind Co-coordinator, Computational methods in communications studies research group, Fall 2016.

\ind Coordinator, Graduate student book group, Summer 2015, Fall 2015 \& Spring 2016.

\ind Organizer, DH + A Symposium at University of Wisconsin-Madison, November 8, 2013. 

\ind Moderator, University of Wisconsin-Madison Undergraduate Research Symposium, April 2013.

\ind Member, University of Wisconsin-Madison Graduate Student Peer Mentor Award Review Committee,
April 2013.

\ind Member, University of Wisconsin-Madison Graduate School Vilas Travel Grant Review Committee,
October 2012 to November 2012.

\ind Moderator, University of Wisconsin-Madison Undergraduate Research Symposium, April 2012.

\ind Member, University of Wisconsin-Madison Statistics Department Social Committee, January 2012 to
May 2014.

\medskip

\noindent\emph{Community service \vspace{0.05in}}

\ind Coach, Madison Science Olympiad Team, November 2013 to March 2014.

\ind Assistant coach, Madison Mathcounts Team, September 2012 to May 2013.

\ind Volunteer, MEDIC, September 2003 to May 2005.

\ind Founder and Director, Salvation Army Learning Center, September 1998 to May 2000.

\ind Cub Scouts Den Leader, Boy Scouts of America, September 1998 to June 2000.

\medskip

\noindent\emph{Professional service \vspace{0.05in}}

\ind Participant, American Statistical Association's Workshop on Communicating with the Media and the Public, November 2016.

\bigskip

\centering
{\tiny Compiled at \currenttime, \today}

\medskip

\end{document}
